The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-21 paper.tex
update

\begin{abstract}
A decade ago, the \textit{Fermi Gamma-Ray Space Telescope} reveals two large bubbles in the Galaxy,\
which extend nearly symmetrically $\sim50^{\circ}$ on either side of the Galactic disk.\

@@

\section{Conclusions}
\label{Conclusions}
%The symmetry of the Galactic bubbles is worth exploring since observations\
%show that there is no preference for the orientation of AGN jets relative to\
%the rotation axis of a galactic plane.

In this work, we introduce a thin, dense disk composed of clumpy interstellar medium\
to divert the inclined jet at an angle $45^{\circ}$\
to the disk normal in the past energetic event of the central SMBH.

>>>>

\begin{abstract}
A decade ago, the \textit{Fermi Gamma-Ray Space Telescope} reveals two large gamma-ray bubbles in the Galaxy,\
which extend nearly symmetrically $\sim50^{\circ}$ on either side of the Galactic disk.\
The recent discovery of eROSITA bubbles also shows a symmetrically enhanced X-ray\
emission from the shells around the eROSITA bubbles.\
To this end, previous simulation-based works assumed that the jets are vertical to the Galactic disk;\
however, there is a lack of preferred orientation of jets with respect to the Galactic disk.\
Using three-dimensional (3D) special relativistic hydrodynamic simulations that\
include cosmic rays (CRs) and thermal gas, we show that a thin interstellar medium disk is an essential\
component for the formation of the symmetrical Galactic bubbles.\
We also produce simulated gamma-ray and\
microwave spectra from the inverse Compton scattering and synchrotron,\
and compare them with the observed counterparts in order to verify\
the oblique jets model.
We find that (1)

@@

\section{Conclusions}
\label{Conclusions}
In this work, we introduce a thin, dense disk composed of clumpy interstellar medium\
to divert the inclined jet at an angle $45^{\circ}$\
to the disk normal in the past energetic event of the central SMBH.
